A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-04 paper.tex
working on 2d

\begin{theorem}
The twist by $Q$ of $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges and matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\Sect(L\times (N_\RR)_{\mr{dR}}, (U\otimes K_L^{1/2})\ham \fg)$. Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
\label{thm:6dCSreduction}
\end{theorem}
\begin{proof}
By Theorem \ref{thm:6dholomorphictwist} the twist of 6d $\cN=(1, 0)$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $\Sect(L\times N, (U\otimes K_L^{1/2})\ham \fg)$. By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\Sect(L\times N_\RR, (U\otimes K_L^{1/2})\ham\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
\end{proof}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.  The fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(\phi_1,\phi_2) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; S \otimes (W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
 \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
 \item Ghost field: $c \in \Omega^0(\RR^2; \gg)[1]$.
\end{itemize}

@@

\begin{proof}
This follows, as in 3d, by dimensionally reducing the holomorphic twist of 3d $\mc N=2$ super Yang-Mills.  That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_to_BF_diml_red_prop} to dimensionally reduce in the real de Rham direction.
\end{proof}

@@

>>>>

\begin{theorem}
The twist by $Q$ of $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges and matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\Sect(L\times (N_\RR)_{\mr{dR}}, (U\otimes K_L^{1/2})\ham \fg)$. Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
\label{thm:6dCSreduction}
\end{theorem}

\begin{proof}
By Theorem \ref{thm:6dholomorphictwist} the twist of 6d $\cN=(1, 0)$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $\Sect(L\times N, (U\otimes K_L^{1/2})\ham \fg)$. By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\Sect(L\times N_\RR, (U\otimes K_L^{1/2})\ham\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
\end{proof}

@@

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=(2,2)$ super Yang-Mills by restricting the fields in dimension 3 from Section \ref{sect:3d_2_section}, or equivalently the 3d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(2;\CC)$.  The fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: $A \in \Omega^1(\RR^2; \gg)$, and a pair of scalars $(\phi_1,\phi_2) \in \Omega^0(\RR^2; \gg \oplus \gg)$.
 \item $R$-valued bosons: $(\Bar{\phi}, \phi) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $(\lambda_+ \otimes u_+,\lambda_- \otimes u_-) \in \Omega^0(\RR^2 ; (S_+ \otimes W_+ \oplus S_- \otimes W_-) \otimes \gg)$.
 \item $R$-valued fermions: $(\psi^+_+,\psi^+_-, \psi^-_+, \psi^-_-) \in \Omega^0(\RR^2 ; (S_+ \oplus S_-) \otimes R \oplus (S_+ \oplus S_-) \otimes R^*)$.
 \item Ghost field: $c \in \Omega^0(\RR^2; \gg)[1]$.
\end{itemize}

@@

\begin{proof}
The statement about the equivalence of the underlying $\ZZ/2\ZZ$-graded theories follows from applying dimensional reduction (Theorem \ref{CS_to_BF_diml_red_prop}) to Theorem \ref{3d_minimal_twist_thm} calculating the minimal twist of 3d $\mc N=2$ super Yang-Mills on $\CC \times \RR_{\mr{dR}}$.  This equivalence is $\mr U(1)$-equivariant.  It is also $\ZZ$-graded, using the twisting datum $\alpha = \phi_A$.
\end{proof}

@@

To deform the holomorphic twist to the topological A-twist, obtaining a Hodge deformation, we use similar techniques to those of Section \ref{sect:4d2Donaldson}.  We first analyze how the supersymmetry action decomposes.  Consider the 1-parameter family of supercharges
\begin{equation} \label{eq:2dHodgefamily}
Q_t = Q_0 + tQ',
\end{equation}
where $Q_0 = (1,i) \in S_+$ is a holomorphic supercharge, and $Q' = (1,i) \in S_-$.  This family of supercharges are all compatible with the twisting homomorphism $\phi_A$ -- the map $\U(1) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$.  They are promoted to twisting data using the homomorphism $\phi_B$ with weights $(1,-1)$.  Let us first decompose our fields according to the twisting homomorphism $\phi_A$.  The fields we obtain are given as follows, where the subscripts denote the $\mr U(1)$-weight.
\begin{itemize}
 \item $\gg$-valued bosons: $(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^4)$.
 \item $R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item $\gg$-valued fermions: $(\lambda_2, \lambda_0, \lambda'_{0}, \lambda_{-2}) \in \Omega^0(\RR^2 ; \gg[-1] \oplus \gg[-1] \oplus \gg[1] \oplus \gg[1])$.
 \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
 \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
\end{itemize}

\begin{prop}
Suppose $Q_t$ is the rank $(1,1)$ supercharge of \ref{eq:2dHodgefamily}.
The $\U(1)$ decomposition of the functionals $I_{\rm gauge}^{(1)}, I^{(1)}_{\rm matter}, I^{(2)}_{\rm gauge}, I^{(2)}_{\rm matter}$ (see \eqref{eq:gaugeI1},  \eqref{eq:gaugeI2}, \eqref{eq:matterI1}, \eqref{eq:matterI2}) in terms of the fields of 2d $\cN=(2,2)$ super Yang--Mills theory are
\begin{align*}
I_{\rm gauge}^{(1)}(Q_t) &= \int \dvol \left(\frac 12((\rho(\dd_{A_1}A_1), \lambda_{-2}^*) + (\rho(\dd_{A_1}\chi_{-1}), \lambda_0^*)) -t(\lambda_{-2}, A^*_1) + (\lambda_0, \chi^*_{-1})) \right)  \\
I^{(2)}_{\rm gauge} (Q_t, Q_t) &= \int \dvol  \\
I_{\rm matter}^{(1)}(Q_t) &= \int \dvol  \\
I_{\rm matter}^{(2)}(Q_t) &= \int \dvol .
\end{align*}
\end{prop}
